IGAS Project

### 2024-04-03 Sections/IGAS.qmd
copy some of the data files over
render full

```{r}
#| label: fig-taskSpace
#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase. This empirical solution space was compiled from all of the participants in experiment 2. Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
#| 
taskspace <- e2 %>% filter(AbsDistFromCenter<900)
taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")

@@

ss
fs

>>>>

```{r}
#| label: fig-taskSpace
#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase. This empirical solution space was compiled from all of the participants in experiment 2. B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
#| fig-width: 11
#| fig-height: 9
#| 
taskspace <- e2 %>% filter(AbsDistFromCenter<900)
taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")

@@

library(patchwork)
ss/fs
